Analysing the three-dimensional structure of P. falciparum

### 2017-07-03 doc/manuscript/paper.tex
more on VE model
Now using DGJIB's template

\documentclass[oupdraft]{bio}
% \usepackage[colorlinks=true, urlcolor=citecolor, linkcolor=citecolor, citecolor=citecolor]{hyperref}
\usepackage{url}

% Add history information for the article if required
\history{Received XXX;
revised XXX;
accepted for publication XXX}

@@

% Title of paper
\title{Analysing the three-dimensional structure of \em{P. falciparum}}

% List of authors, with corresponding author marked by asterisk
\author{Nelle Varoquaux$^\ast$,\\[4pt]
% Author addresses
\textit{Department of Statistics, University of California, Berkeley \\
Berkeley Data Science Fellow}
\\[2pt]
% E-mail address for correspondence
{nelle@berkeley.edu}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{Nelle Varoquaux}
% Second field is the short title of the paper
{XXX}

\maketitle

% Add a footnote for the corresponding author if one has been
% identified in the author list
\footnotetext{To whom correspondence should be addressed.}

\begin{abstract}
{My very cool abstract.}
{Hi-C; three-dimensional structure; and other cool stuff.
}
\end{abstract}

@@

@@

\bibliographystyle{biorefs}
\bibliography{refs}

>>>>

%\documentclass[2columns]{article}

\documentclass[letterpaper,12pt]{article}
\usepackage{url}
\usepackage{graphicx}
\usepackage{url}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{xr}

\usepackage{amsmath,amssymb,amsfonts,amscd,latexsym}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{eurosym}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{xspace}

% Two column foonotes
\usepackage{dblfnote}

%% This is the recommended preamble for your document.

%% Load De Gruyter specific settings 
\usepackage{dgjournal}

%% The mathptmx package is recommended for Times compatible math symbols.
%% Use mtpro2 or mathtime instead of mathptmx if you have the commercially
%% available MathTime fonts.
%% Other options are txfonts (free) or belleek (free) or TM-Math (commercial)
\usepackage{mathptmx}

%% Use the graphics package to include figures
\usepackage{graphics}

%% Use natbib with these recommended options
\usepackage[authoryear,comma,longnamesfirst,sectionbib]{natbib}

%\externaldocument{supp}

@@

% Title of paper
\title{Analysing the three-dimensional structure of P. falciparum}
\author{Nelle Varoquaux}

%\maketitle

\begin{abstract}

\end{abstract}

@@

We use IMP to generate a population of structures.

\paragraph{Adding constraints on VRSM genes}

@@

\bibliographystyle{DeGruyter}
\bibliography{refs}
